Calculate FD

### 2020-07-03 analysis/calc_fd.Rmd
save fd data for null model as csv, only include plots that meet the criteria for inclusion.

  fd_out <- as_tibble(dbFD_joggle(trait_mat, species_mat, w.abun = FALSE))[,1:8] %>%
    cbind(years, .) %>%
    mutate(plot_id = unlist(filter_plot), trait_count = dim(trait_mat)[2]) %>%
    write_tsv(paste0(here::here("data"), "/fd_output/", filter_plot, "_fd.tsv"))

>>>>

  fd_out <- as_tibble(dbFD_joggle(trait_mat, species_mat, w.abun = FALSE))[,1:8] %>%
    cbind(years, .) %>%
    mutate(plot_id = unlist(filter_plot), trait_count = dim(trait_mat)[2])
    write_tsv(fd_out, paste0(here::here("data"), "/fd_output/", filter_plot, "_fd.tsv"))
